---
title: "Rmarkdown_example"
author: "Jeremy Hogeveen"
date: "2026-03-02"
output: html_document
---

```{r setup, include=FALSE}
# boilerplate knitr step
knitr::opts_chunk$set(echo = TRUE)
# Load tidyverse
library(tidyverse)
```

## R Markdown

* This is an `R` Markdown document. 
* using the default output of `.html`, though `.pdf` is also an option.
* We're going to run the same steps as our RStudio example, but showing how it looks in Markdown
  * same principles / formatting as Jupyter lab `markdown` chunks!

```{r simulate_data}
# Simulate some RTs on an explore-exploit task
set.seed(42)
task_data <- tibble(
  trial = 1:100,
  condition = rep(c("Explore", "Exploit"), each = 50),
  rt_ms = c(rnorm(50, mean = 650, sd = 100), rnorm(50, mean = 400, sd = 80))
)

# Look at the first few rows
head(task_data)
```

## Plotting the data

* Now, when we run our ggplot2 code, the code and plots will appear in sequence in the markdown output.

```{r plot_data}
# Plot the results
ggplot(task_data, aes(x = condition, y = rt_ms, fill = condition)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Reaction Times: Explore vs. Exploit", y = "Reaction Time (ms)")
```